%General file for CV
\documentclass[margin,10pt]{res}
\setlength{\textwidth}{6in}
\addtolength{\oddsidemargin}{-.475in}
\addtolength{\evensidemargin}{-1.875in}% length of text
\usepackage{hyperref}
\usepackage[T1]{fontenc}
\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
% \setlength{\parskip}{0pt}
% \setlength{\parsep}{0pt}
% \setlength{\headsep}{0pt}
% \setlength{\topskip}{0pt}
% \setlength{\topmargin}{0pt}
% \setlength{\topsep}{0pt}
% \setlength{\partopsep}{0pt}
\newcommand{\subs}[1]{\normalfont\emph{\color{Black!90}#1}}
\newcommand{\secs}[1]{\normalsize{\section{\subs{#1}}}}
\begin{document}

% personal information
\moveleft.5\hoffset\centerline{\large\bf Dami\'an Pablo (San Rom\'an Alerigi)}
\moveleft.5\hoffset\vbox{\hrule width 6in height 1pt}\smallskip
\moveleft.5\hoffset\centerline{a: 4700 KAUST, P. O. Box 1850, Thuwal, 23955-6900, Kingdom of Saudi Arabia.}
\moveleft.5\hoffset\centerline{m: +966 544 700 801, e: \href{mailto:damian.sanroman@kaust.edu.sa}{damian.sanroman@kaust.edu.sa} }

%objective
%\section{Purpose} Ph. D. Activity report

% \section{Personal information}
% \normalsize{~}
% \normalsize{\section{\subs{Date of birth}} 13 August 1985
% \section{\subs{Place of birth}} Buenos Aires, Argentina
% \section{\subs{Nationality}} Argentina, Mexico
% \section{\subs{International experience}} lived in Argentina, Brazil, Uruguay, Mexico, United States, Spain, and Saudi Arabia}

\section{Education}

\secs{~~}
\normalsize{\section{\subs{Degree}}}
Licenciatura in Physics (physicist).
\normalsize{\section{\subs{Institution}}}
College of Sciences, \emph{National Autonomous University of Mexico} (UNAM), Coyoac\'an, Mexico
% {\bf Major Subjects}\\
% \begin{ncolumn}{2}
% 	\hline
%     Quantum mechanics         	&  Classical Mechanics \\
%     Thermodynamics 				&  Statistical Physics \\
%     Electrodynamics				&  Classical wave optics \\
%     Relativity 					&  Quantum optics \\
%     Intro. to hydrodynamics 	&  Advance mathematics for physics \\
% 	Real analysis 				&  Complex analysis \\
% 	Ordinary differential equations & Partial differential equations \\
% 	\hline
% \end{ncolumn}
\secs{Major subjects}
\begin{ncolumn}{3}
	\hline
    Quantum mechanics         	&  Classical Mechanics 	&  Thermodynamics \\ 
    Statistical Physics 		&  Electrodynamics		&  Classical wave optics \\
    Relativity 					&  Quantum optics 		&  Intro. to hydrodynamics \\
    Real analysis				&  Complex analysis 	&  Ordinary differential equations \\
    Partial differential equations & Intro. to differential geometry & Adv. math for physics \\
	\hline
\end{ncolumn}
\secs{Dates}
September 2003 to March 2009\\

\secs{Degree} Master in Science
\secs{Institution} Electrical Engineering department, \emph{King Abdullah University of Science and Technology} (KAUST), Thuwal, Saudi Arabia 
\secs{Major subjects}
\begin{ncolumn}{2}
	\hline
    Semiconductor optoelectronic devices	&  Semiconductor Lasers and LEDs \\ 
    Numerical methods 			&  Electromagnetics \\
    Optics 	&  Introduction to MEMS \\
    \hline
\end{ncolumn}
\secs{Dates} September 2009 to December 2010\\

\secs{Degree} Philosoph\ae~Doctor, Ph. D.
\secs{Institution} Electrical Engineering department, \emph{King Abdullah University of Science and Technology} (KAUST), Thuwal, Saudi Arabia
\secs{Research topic} Light control, manipulation and transformation for photonic integrated circuits (PICs)
\secs{Major achievements}
\begin{itemize}
	\item Study of the transient photon and electron induced refractive index modification in chalcogenide materials
	\item Study of planar refractive index maps for light trapping and confinement (solution to the inverse scattering problem in the paraxial approximation)
	\item Study of planar refractive index maps for light transformation (solution inverse electromagnetic problem for full vectorial description)
	\item Development of numerical toolbox for the study of wave propagation in time-varying, non-linear, anisotropic and heterogeneous materials  
\end{itemize} 

\secs{Dates} January 2011 to August 2014 (expected graduation date) \\


\section{Personal Skills \& Qualifications}

\secs{~~}
\secs{Languages}
Spanish (proficient), English (proficient), French (mid-level).

\secs{Computer}
Proficient programming in Matlab, Mathematica, Fortran, Python, COMSOL, knowledge of high performance computing, with speciality in FEM and FDTD methods for \emph{wave propagation in time-dependant \& heterogeneous materials},  \emph{inverse problem solutions to the wave equation in heterogeneous media}, and \emph{transformation optics} 

\secs{Technical}
Laser Safety, Laboratory Safety, Cleanroom Laboratory Safety, scanning electron microscopy (SEM), and focus ion beam (FIB), pulsed laser deposition (PLD), electron beam deposition (e-beam), photon and Ramman spectroscopy.

\secs{Organizational and social}
Teamwork, leadership, good ability to adapt  in multicultural environments, communication, logistics and strategic development.

\secs{Artistic}
Piano and music theory (14 years training), writing and literature (2 years coursework and training), photography (4 years training in workshops and coursework).\\


\section{Professional profile}

\secs{~~}
\secs{Fellowships and appointments}
\begin{tabular}{p{3.8in} l}
%Description & Period \\
%\hline
Junior Research Fellow \newline Advanced Optics Laboratory, College of Sciences UNAM \newline Description: experiments in quantum optics, development of a novel measurement strategy for concurrent triple coincidences and theory on properties of vacuum states \newline Supervisor: Victor M. Velazquez (vicvela@ciencias.unam.mx) \newline ~ & September 2006 to August 2009 
\end{tabular}

\begin{tabular}{p{3.8in} l}
Research Fellow \newline Joint Quantum Institute, Atomic and Molecular Optics Laboratory, University of Maryland at College Park \newline Description: Development of laser control system for quantum state measurement and preparation \newline Supervisor: Luis L. Orozco (lorozco@umd.edu) \newline & March 2007 to September 2007 \end{tabular}

\begin{tabular}{p{3.8in} l}
Research Fellow \newline Institut de Ciencies Fotoniques (ICFO) \newline Description: Development of a fast polarimetry system and density function measurement device for quantum states characterization \newline Supervisor: Morgan Mitchell (mmitchell@icfo.es) \newline & March 2008 to October 2008
\end{tabular}

\begin{tabular}{p{3.8in} l}
Student Research Fellow \newline KAUST Photonics Laboratory, KAUST \newline Description: Numerical study of strategies for light trapping, confinement and transformation in planar refractive index structures. Development of a high performance library for the solution of wave propagation in superluminal perturbations, and time-varying-heterogeneous-anisotropic-non-linear materials \newline Supervisor: Boon S. Ooi (boon.ooi@kaust.edu.sa) \newline & September 2009 - today 
\end{tabular}

\begin{tabular}{p{3.8in} l}
Research Fellow \newline Estrategia y Desarrollo A.C. \newline Description: consultant on development strategies for clusterization \newline Supervisor: Gerardo San Roman M (gerardosrm@itesm.mx) \newline & December 2011 - today
\end{tabular}


\secs{Education and teaching}
February - July 2006 Teacher assistant for Electrodynamics II at UNAM College of Sciences,\\
September - December 2011 Teacher assistant for Introduction to Statistics  (AMCS 210), KAUST,\\
September - December 2012 Teacher assistant for Introduction to Statistics  (AMCS 210), KAUST.\\



\section{Publications}
\secs{Journals}
D. P. San-Roman-Alerigi, D. H. Anjum, Y. Zhang, X. Yang, A. B. Slimane, T. K. Ng, M. Alsunaidi, and B. S. Ooi, \emph{Electron irradiation induced reduction of the permittivity in Chalcogenide glass (As2S3) thin film}, Journal of Applied Physics, vol. 113, 044116, 2013.

D. P. San-Roman-Alerigi, T. K. Ng, M. Alsunaidi, Y. Zhang, and B. S. Ooi, \emph{Generation of $J_0$-Bessel-Gauss beam by an heterogeneous refractive index map}, Journal of the Optical Society of America A,vol. 29, pp. 1252 -- 1258, 2012.



\secs{Conferences}
D. P. San-Roman-Alerigi, A. B. Slimane, T. K. Ng, M. Alsunaidi, and B. S. Ooi, \emph{On a pragmatic approach to optical analogues of gravitational attractors}, Proceedings of Photonics Global Conference (PGC), Singapore, December 2012

D. P. San Roman Alerigi,T.K. Ng,  Y. Zhang, A. B. Slimane, and B. S. Ooi, \emph{Monolithic Silicon-based Gauss to J0 Bessel Beam Conventer}, Proceedings of PIERS 2012, Malaysia, 2012.

Yaping Zhang, Damian P. San Roman Alerigi, Tien Khee Ng, Boon S. Ooi, \emph{Building Blocks of Passive Optical Components Fabricated in Pulsed Laser Deposited As2S3 Chalcogenide Glass Film}, Proceedings of ICMAT 2011, Singapore, 2011.

Hisham Al-Falih, Yasser Khan, Yaping Zhang, Damain San-Roman-Alerigi, Dongkyu Cha, Boon S. Ooi and Tien Khee Ng, \emph{Fabrication of Tuning-fork Based AFM and STM Tungsten Probe}, Proceedings of HONET 2011, Saudi Arabia, 2011.

Yaping Zhang, Yangqin Gao, Damian P. San Roman Alerigi, Tien K. Ng, and Boon S. Ooi, Basil Chew and Mohamed Nejib Hedhili, Donghui Zhao and Himanshu Jain, \emph{Engineering of Refractive Index in Sulfide Chalcogenide Glass by Direct Laser Writing}, PGC 2010, art. no.: 5705967, Singapore, Dec 2010.

D. P. San Roman Alerigi, N. Guerrero, and G. San Roman M., \emph{La Clusterización como Estrategia para el
Desarrollo Económico y Social de una Región, Cluster del Conocimiento}, TCI 15th Annual Conference, Spain, 2012.

\secs{Books & contributions}


\section{Awards}
2007 UMD-REU Research Scholarship,\\ 
2008 Caixa Catalunya – ICFO Research Scholarship,\\ 
2008 UNAM-PAPIIME Research Scholarship,\\
2008 KAUST Discovery Scholar,\\
2009 KAUST Provost Award,\\
2010 KAUST Academic Excellence Award.\\

\section{Extra-curricular activities}
Co-founder, UNAM Holography Workshop Laboratory. March 2007,\\
Co-founder, Student Emergency Council at KAUST, September 2009, \\
Co-founder, University Relations Chair of the KAUST  Graduate Student Council, November 2009, \\
Co-founder,  \emph{Estrategia y Desarrollo, A.C.}, January 2011\\
Vice-President, KAUST  Graduate Student Council, November 2012 \\ 
Founder - \emph{les souvenirs heureux}, professional photography & experimental literature project\\


\section{Affiliations}
2009 Founding Scholar - King Abdullah University of Science and Technology\\
2009 Founding Chair - KAUST Graduate Student Council\\
2010 Member -- Institute of Electric and Electronic Engineers,\\
2011 Member -- American Physical Society,\\
2012 Member -- Optical Society of America,\\
2012 Member -- Society for Industrial and Applied Mathematics,\\
2012 Member -- Sociedad Mexicana de Física,\\
2012 Member -- The Competitiveness Institute 


\end{document}